---
title: "Antennas in The Netherlands"
subtitle: "A leaflet demo"
author: "Hugo van den Berg"
date: "2 oktober 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

## Introduction

This document features an interactive map of the Netherlands depicting all
registered antennas with their respective height and purpose, as well as the
municipality it is registered in.

```{r load_libraries, echo=FALSE}
library(magrittr) # v1.5
library(dplyr) # v0.5.0

library(htmltools) # v0.3.5
library(leaflet) # v1.0.1
library(rgdal) # v1.1-10
```

## Data

The data is available from [Imergis](http://www.imergis.nl/asp/47.asp) (in
Dutch), which is a site listing publicly available geographic data including
administrative borders, infrastructure, and point objects such as important
buildings, and of course the *Antenneregister*.
The dataset contains the name of the municipality, purpose, coordinates and
height in meters.

```{r load_data}
# Download file if it's missing
if (!file.exists('./gisdata/2015-09-Antenneregister-RD.shp')) {
    dataurl <- 'http://www.imergis.nl/shp/2015-09-Antenneregister-RD-shp.zip'
    localzip <- '2015-09-Antenneregister-RD-shp.zip'
    download.file(dataurl, localzip)
    unzip(localzip, exdir = './gisdata')
}
antennas <- readOGR(
    dsn = './gisdata', # For shapefiles point at directory above
    layer = '2015-09-Antenneregister-RD', # Shapefile name
    verbose = FALSE # Hide output
    )

# Convert coordinates from Dutch Rijksdriehoek to WGS84 (EPSG:4326)
antennas84 <- antennas %>% spTransform(CRS('+init=EPSG:4326'))

# Labels (%<>% is an advanced pipe operator from the magrittr package)
antennas84@data %<>%
    mutate(LABEL = paste0('Purpose: ', htmlEscape(TOEPASSING),
                          '<br/>Municipality: ', htmlEscape(GEMEENTE),
                          '<br/>Height: ', htmlEscape(ANT_HOOGTE), ' m'))
```

## Plotting

To plot the `r nrow(antennas84)` antennas on the map we use the leaflet
library, clustering them when zoomed out.

```{r leaflet, out.width=910,dpi=150}
antennas84 %>%
    leaflet() %>%
    addTiles()%>%
    addMarkers(popup = antennas84$LABEL,
               clusterOptions = markerClusterOptions())
```

## Libraries

This document was built using the following libraries:

```{r load_libraries}
```
